Unit 1_Assignment
1. Calculate
a. 
// With loop
```{r}
temp <- 0
sum <- 0
for (i in 5:100) {
  temp = i^4 + 5*i^3
  sum = sum + temp
}
sum
```
// without loop
```{r}
i <- 5:100
result <- sum(i^4 + 5*i^3)
result
```
b. Calculate U40
```{r}
y <- seq(3, 40, by=1)
res_list <- list(1,2)
temp <- 0
for (i in y) {
  pos1 = i-1
  pos2 = i-2
  temp = as.integer(res_list[pos1]) + as.integer(res_list[pos2])
  res_list <- c(res_list, temp)
}
sprintf("U40 = %d", as.integer(res_list[40])) 
```

c. Program to calculate cosx, sinx(Taylor series)
```{r}
x <- as.integer(readline(prompt = "Enter x value: "))
n <- seq(0, 45, by = 1)
sin_result <- sum(((-1)^n * x^(2*n+1))/factorial(2*n + 1))
sin_result
cos_result <- sum(((-1)^n * x^(2*n))/factorial(2*n))
cos_result
# This is not correct, will be correct later.
```

d. a vector of the value of e^x cos(x) at x = 3,3.1,3.2,....6
```{r}
x <- seq(3, 6, by = 0.1)
expected_vector <- exp(x) * cos(x)
expected_vector
```
e.
```{r}
x <- 1:3000
num <- 0
temp <- 0
for (i in x) {
  temp = i %% 2
  if (temp != 0) {
    num = num
  } else {
    num = num + 1
  }
}
num
```
2. Solve linear equation using Gaussian elimination
```{r}
A <- matrix(c(1, 2, 3, 2, -1, 2, 3, 3, 1), 3, 3, byrow = TRUE)
B <- matrix(c(9, -3, 5),nrow = 3, ncol = 1)
res <- rref(cbind(A, B))
res
sprintf("x = %.2f", res[10])
sprintf("y = %.2f", res[11])
sprintf("z = %.2f", res[12])
```
3. use outer function to create matrix
```{r}
x <- 0:4
y <- 0:4
mat <- outer(x, y, function(x, y) x + y)
mat
```
4.
a. Data Source detail
link: https://www.kaggle.com/shashwatwork/impact-of-covid19-pandemic-on-the-global-economy

b. There are 9 variables in the dataset.
- iso_code: it is the code for each country.
- location: it is the country name.
- Date: the date in the data set is from 2019-12-31 to 2020-10-19.
- total_cases: number of people who is sick
- total_deaths: number of people died
- stringency_index: it is a score assigned to countries by Oxford. The score is between 0 and 100. The higher score determines the strongest lockdown. 
- population: the number of citizens in the country.
- gdp_per_capita: it is a metric that breaks down a country's economic output per person.
- human_development_index: a summary measure of average achievement in key dimensions of human development(a long and healthy life, being knowledgeable and have a decent standard of living).

c.find the missing values and replace by mean value
```{r}
dt <- read_csv("impact_covid_ecomic.csv")
apply(is.na(dt),2,which)
dt <- impute(dt)
```

d. generate 2 new variables
```{r}
dt <- mutate(dt, Mean <- mean(total_cases + total_deaths))
dt <- mutate(dt, Median <- total_cases + total_deaths)
```

e. rename two existing variables
```{r}
dt <- rename(dt, HDI = human_development_index)
dt <- rename(dt, Pop = population)
dt
```

f. create plot
```{r}
ggplot(dt, mapping=aes(x=iso_code,y=gdp_per_capita)) + geom_point(size=5, color = "red", alpha = 1/5)+ geom_smooth(method = "lm") + facet_grid() + coord_cartesian() + xlab("country") + ylab("GDP")
ggtitle("gdp around the world in pandemic")
ggsave(filename="D:/Lecture/Mr. Dinesh/Semester_7/covid_19_dataset1.png", units = "cm", width = 25, height = 25)
```
I didn't pass any argument in facet_grid(). If I pass any argument, the plot is hard to understand since the dataset has lots of rows.

